---
title: "AFV Capstone Project"
author: "Kayla Shinevar"
date: "2023-07-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Alternative Fuel Vehicles Exploratory Data Analysis

In this data analytics project, I explore the landscape of alternative fuel vehicles (AFVs) in the United States using multiple datasets. By analyzing AFV registrations by state, alternative fuel/charging station availability, and various AFV models, I aim to gain insights into the adoption of alternative fuel vehicles and the growth of charging infrastructure. I hypothesize that states with a higher number of alternative fuel/charging stations will have a higher number of AFV registrations. Throughout the analysis, I leverage SQL for data processing and Tableau for visualization, providing clear and interactive representations of the data trends and relationships. This project showcases my proficiency in SQL and Tableau while investigating an essential aspect of sustainable transportation.

## Process

Below is a detailed step by step of my process used to complete this analysis.

### 1. Gather Data

In order to begin my project, I needed to find some datasets on Alternative Fuel Vehicles. I was able to find several easily downloadable datasets from the Alternative Fuels Data Center website: https://afdc.energy.gov/

I also found a great table containing AFV registration counts by state and fuel type [here](https://afdc.energy.gov/vehicle-registration). They have this table for the years 2016-2022.

Unfortunately, there was not a downloadable version of these tables so I needed to scrape it using rSelenium.

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
